---
title: "R Notebook"
output: html_notebook
---

# Dirty Data - Louise Shambrook
## 26/11/2021

### - Required libraries
```{r}
library(readr)
library(readxl)
library(dplyr)
library(here)
#calling libraries
```

## Points to include in final report:
- A brief introduction to the dataset
- A list of any assumptions you have made
- The steps you took to clean the data (you don’t need to write out in detail every step, but a combination of commented code chunks with surrounding overall explanations would be great).
- The answers to the questions presented in the task brief
- Any other interesting analyses or conclusions you come across.

# Final report (draft)

### Brief Introduction to the dataset
In 2006, David Ng and Ben Cohen began to rank candy based on their location
in geological strata, for trick or treating purposes. This has developed over
the years into a "not quite social science legit survey". As of 2019, this has 
become a way of measuring "net feelies" when trick or treating, for a wide range
of candies, which critically includes items such as hugs, glow sticks and bread.

Source: https://boingboing.net/author/davidng2

### Brief introductions to assumptions
- I intially assumed the dataset was complete, i.e. that the columns were correct
(should be there).
- As I began to dig in to it and opened it in excel, I learned that some of
these could be dropped.
- I then over-corrected and tried to drop too many.
- I then began to research the background of the dataset, and found that only
some of these would need to be dropped.
- I assume that many of the NA's can be dropped/changed without causing many problems.
- I assume that respondents will generally only be from the US and Canada.
- I assume that age will only be given in whole numbers.

### Steps to clean the data
- Changing names of columns
- Changing timestamp of 2015 and 2016
- Changing column type of age

## Analysis

What is the total number of candy ratings given across the three years.
(Number of candy ratings, not the number of raters. Don’t count missing values)
```{r}
group_by
summarise(across(count))
```

What was the average age of people who are going out trick or treating?
```{r}
filter(going_out = yes)
group_by(age)
summarise(mean(age))
```

What was the average age of people who are not going trick or treating?
```{r}
filter(going_out = no)
group_by(age)
summarise(mean(age))
```

For each of joy, despair and meh, which candy bar received the most of these ratings?
```{r}

```

How many people rated Starburst as despair?
```{r}

```

For the next three questions, count despair as -1, joy as +1, and meh as 0.
What was the most popular candy bar by this rating system for each gender in
the dataset ?
```{r}
filter(f)
group_by(across(all(joy)))
summarise(sum(n))

```

What was the most popular candy bar in each year?
```{r}

```

What was the most popular candy bar by this rating for people in US, Canada,
UK, and all other countries?
```{r}

```

