---
title: "R Notebook"
output: html_notebook
---

NOTE TO MYSELF - WHEN I PICK UP ON TUESDAY - MOVE NOTES OVER FROM HERE to R SCRIPT

## TO DO
- Assertive programming
- Unit tests


# Dirty Data - Louise Shambrook
## 26/11/2021

### - Required libraries
```{r}
library(readr)
library(readxl)
library(dplyr)
library(here)
library(janitor)
library(stringr)
library(tidyverse)
library(assertr)
#calling libraries
```

```{r}
names(candy_2015)
```

## Points to include in final report:
- A brief introduction to the dataset
- A list of any assumptions you have made
- The steps you took to clean the data (you don’t need to write out in detail every step, but a combination of commented code chunks with surrounding overall explanations would be great).
- The answers to the questions presented in the task brief
- Any other interesting analyses or conclusions you come across.

# Final report (draft)

### Brief Introduction to the dataset
In 2006, David Ng and Ben Cohen began to rank candy based on their location
in geological strata, for trick or treating purposes. This has developed over
the years into a "not quite social science legit survey". As of 2019, this has 
become a way of measuring "net feelies" when trick or treating, for a wide range
of candies, which critically includes items such as hugs, glow sticks and bread.

Source: https://boingboing.net/author/davidng2

### Brief introductions to assumptions
- I intially assumed the dataset was complete, i.e. that the columns were correct
(should be there).
- As I began to dig in to it and opened it in excel, I learned that some of
these could be dropped.
- I then over-corrected and tried to drop too many.
- I then began to research the background of the dataset, and found that only
some of these would need to be dropped.
- I assume that many of the NA's can be dropped/changed without causing many problems.
- I assume that respondents will generally only be from the US and Canada.
- I assume that age will only be given in whole numbers.
- That the "random" columns at the end, were indeed random, however upon further
research and reading, I learned that these are indicators for charactor and that
this has an impact on the ratings. I have then begun to think about how I can 
change my data analysis to reflect this, as the time constraints of the project
means that realistically means I will not be able to include all of them.
Source: https://boingboing.net/2015/10/31/the-candy-hierarchy-2015-your.html
Table 1B. 

### Steps to clean the data
- Changing names of columns
- Changing timestamp of 2015 and 2016
- Changing column type of age

## Analysis


```{r}
candy_2015 <- read_xlsx(here::here("raw_data/boing-boing-candy-2015.xlsx"))
candy_2016 <- read_xlsx(here::here("raw_data/boing-boing-candy-2016.xlsx"))
candy_2017 <- read_xlsx(here::here("raw_data/boing-boing-candy-2017.xlsx"))
```

```{r}
# 2015 CLEANING  --------------------------------------------------------------


# 2016 CLEANING ---------------------------------------------------------------


# Change all versions of USA to USA, and similar for other countries.

# Remove incorrect strings. 

# Clean state column, i.e. ensure all strings are correct.

# Change all USA and canadian states to same format, e.g. TN, USA


# 2017 Cleaning --------------------------------------------------------------


# reassigning the internal_id column to 2017

# Cleaning the age column
# There are 2 answers which indicate a specific answer, e.g. "40. Deal with it".
# There are 5 which reference a vague answer, e.g. "50's". It is not
# reasonable to assume their answer - if there is time, I will go back and
# replace these with "vague" (or similar). Then there are the outright "invalid"
# answers, e.g. "old enough" which do not reference an age. These are NA.


# Clean country names; ensure all countries are capitalised.

# Change all versions of USA to USA, and similar for other countries.

# Remove incorrect strings. 

# Clean state column, i.e. ensure all strings are correct.

# Change all USA and canadian states to same format, e.g. TN, USA
```

```{r}
clean_2015 <- clean_names(candy_2015)
clean_2015 <- clean_2015 %>%
  rename(age = how_old_are_you,
         going_out = are_you_going_actually_going_trick_or_treating_yourself,
         year = timestamp,
         hersheys_kissables= hershey_s_kissables,
         hersheys_milk_chocolate = hershey_s_milk_chocolate,
         remarks_or_comments = please_leave_any_remarks_or_comments_regarding_your_choices,
         items_not_included_joy = please_list_any_items_not_included_above_that_give_you_joy,
         items_not_included_despair = please_list_any_items_not_included_above_that_give_you_despair
  )
clean_2015 <- clean_2015 %>%
  relocate(necco_wafers, .after = york_peppermint_patties)
clean_2015$year <- 2015
clean_2015$age[clean_2015$age == "45, but the 8-year-old Huntress and
                 bediapered Unicorn give me political cover and social
                 respectability.  However, I WILL eat more than they do
                 combined."] <- 45
clean_2015$age[clean_2015$age == "37 (I'm taking a child)"] <- 37
clean_2015$age[clean_2015$age == "Good Lord!  I'm 43!"] <- 43
clean_2015$age[clean_2015$age == "46:"] <- 46
clean_2015$age[clean_2015$age == "40. Deal with it. "] <- 40
clean_2015$age[clean_2015$age == "37,"] <- 37
clean_2015$age[clean_2015$age == "50 (despair)"] <- 50
clean_2015$age[clean_2015$age == "27^"] <- 27
clean_2015$age[clean_2015$age == "50, taking a 13 year old."] <- 50
clean_2015$age[clean_2015$age == "42 - I'm taking my kid"] <- 42
clean_2015$age[clean_2015$age == "42 - I'm taking my kid"] <- 42
clean_2015$age[clean_2015$age == "50t"] <- 50                 
clean_2015 <- clean_2015 %>%
  transform(age = as.numeric(age))
clean_2015 <- clean_2015 %>%
  add_column(gender = NA, .after = "going_out") %>%
  add_column(country = NA, .after = "gender") %>%
  add_column(state = NA, .after = "country")
clean_2015 <- clean_2015 %>%
  select(-101, -102, -103, -104, -105, -106, -107, -108, -109, -110, -111, 
         -112, -113, -114, -115, -116, -117, -118, -119, -120, -121, -122,
         -123, -124, -125, -126, -127)

## THIS IS MY ATTEMPT AT ASSERTIVE PROGRAMMING - ASK SOMEONE LATER
# clean_data_2015_age <- function(age_people) {
#   #check age
#   age_people %>%
#     verify(age >0 & age <= 80)
#   
#   #average_age
#   average_age <- 
#     age_people %>%
#     summarise(
#       mean_age = mean(age)
#     )
#   return(list(mean_age))
# }    
#assertive programming function  

clean_2015 <- clean_2015 %>%
  mutate(age = na_if(age, 1.23000e+02)) %>%
  mutate(age = na_if(age, 9.00000e+22)) %>%
  mutate(age = na_if(age, 1.88000e+03)) %>%
  mutate(age = na_if(age, 2.00587e+05)) %>%
  mutate(age = na_if(age, 9.90000e+01)) %>%
  mutate(age = na_if(age, 1.00000e+02)) %>%
  mutate(age = na_if(age, 1.15000e+02)) %>%
  mutate(age = na_if(age, 3.88000e+02)) %>%
  mutate(age = na_if(age, 1.20000e+02)) %>%
  mutate(age = na_if(age, 1.08000e+02)) %>%
  mutate(age = na_if(age, Inf)) %>%
  mutate(age = na_if(age, 9.90000e+01)) %>%
  mutate(age = na_if(age, 2.00000e+03)) %>%
  mutate(age = na_if(age, 3.50000e+02)) %>%
  mutate(age = na_if(age, 4.00000e+02)) %>%
  mutate(age = na_if(age, 8.50000e+01)) %>%
  mutate(age = na_if(age, 9.70000e+01)) %>%
  mutate(age = na_if(age, 4.90000e+02)) %>%
  mutate(age = na_if(age, 350))

```

```{r}
clean_2016 <- clean_names(candy_2016)
clean_2016 <- clean_2016 %>%
  rename(age = how_old_are_you,
         going_out = are_you_going_actually_going_trick_or_treating_yourself,
         year = timestamp,
         gender = your_gender,
         country = which_country_do_you_live_in,
         state = which_state_province_county_do_you_live_in,
         hersheys_milk_chocolate = hershey_s_milk_chocolate,
  )
clean_2016 <- clean_2016 %>%
  transform(age = as.numeric(age))
clean_2016$year <- 2016
clean_2016 <- clean_2016 %>%
  relocate(age, .after = year)
clean_2016 <- clean_2016 %>%
  select(-107, -108, -109, -110, -111, 
         -112, -113, -114, -115, -116, -117, -118, -119, -120, -121, -122,
         -123)

clean_2016 <- clean_2016 %>%
  mutate(country = str_to_title())

# cleaning USA
clean_2016 <- clean_2016 %>%
  mutate(country = str_replace(country, "[u][sS][aA]", "USA")) %>%
  mutate(country = str_replace(country, "[uU][s]", "USA")) %>%
  mutate(country = str_replace(country, "^US$", "USA")) %>%
  mutate(country = str_replace(country, "^Usa$", "USA")) %>%
  mutate(country = str_replace(country, "^USA!", "USA")) %>%
  mutate(country = str_replace(country, "^USA USA USA$", "USA")) %>%
  mutate(country = str_replace(country, "[U][s][a]", "USA")) %>%
  mutate(country = str_replace(country, "^Usa!$", "USA")) %>%
  mutate(country = str_replace(country, "[U][.][S][.][A][.]", "USA")) %>%
  mutate(country = str_replace(country, "^United States of America$", "USA")) %>%
  mutate(country = str_replace(country, "[uU][n][i][t][e][d][ ][Ss][t][a][t][e][s]", "USA")) %>%
  mutate(country = str_replace(country, "^Murica$", "USA")) %>%
  mutate(country = str_replace(country, "^U.S.$", "USA")) %>%
  mutate(country = str_replace(country, "^USA USA! USA!", "USA"))

# removing NA/not input countries
clean_2016 <- clean_2016 %>%
  mutate(country = na_if(country, "A tropical island south of the equator")) %>%
  mutate(country = na_if(country, "Neverland")) %>%
  mutate(country = na_if(country, 51.0)) %>%
  mutate(country = na_if(country, 47.0)) %>%
  mutate(country = na_if(country, 54.0)) %>%
  mutate(country = na_if(country, 44.0)) %>%
  mutate(country = na_if(country, 45.0)) %>%
  mutate(country = na_if(country, 30.0)) %>%
  mutate(country = na_if(country, "one of the best ones")) %>%
  mutate(country = na_if(country, "there isn't one for old men")) %>%
  mutate(country = na_if(country, "god's country")) %>%
  mutate(country = na_if(country, "see above")) %>%
  mutate(country = na_if(country, 45.0)) %>%
  mutate(country = na_if(country, "this one")) %>%
  mutate(country = na_if(country, "somewhere"))

# clean_2016 %>%
#   filter(country != "USA", country != "Canada", country != "UK", country != "United Kingdom",
#          country != "Japan", country != "france")

# Note - this is incomplete.

clean_2016 <- clean_2016 %>%
  mutate(age = na_if(age, 8.10e+01)) %>%
  mutate(age = na_if(age, 1.00e+18)) %>%
  mutate(age = na_if(age, 8.20e+01)) %>%
  mutate(age = na_if(age, 1.42e+02))

```

```{r}
clean_2017 <- clean_names(candy_2017)
clean_2017$year <- 2017
clean_2017 <- clean_2017 %>%
  rename(going_out = q1_going_out,
         gender = q2_gender,
          age = q3_age,
          country = q4_country,
          state = q5_state_province_county_etc)
clean_2017 <- clean_2017 %>%
  select(-110, -111, -112, -113, -114, -115, -116, -117, -118, -119, -120, -121)
clean_2017 <- clean_2017 %>%
  rename(year = internal_id)
clean_2017$age[clean_2017$age == "sixty-nine"] <- 69
clean_2017$age[clean_2017$age == "46 Halloweens"] <- 46
clean_2017 <- clean_2017 %>%
  relocate(age, .after = year)
clean_2017$internal_id <- 2017
clean_2017 <- clean_2017 %>%
  transform(age = as.numeric(age))

clean_2017 <- clean_2017 %>%
  mutate(age = na_if(age, 90)) %>%
  mutate(age = na_if(age, 312)) %>%
  mutate(age = na_if(age, 99)) %>%
  mutate(age = na_if(age, 88)) %>%
  mutate(age = na_if(age, 102)) %>%
  mutate(age = na_if(age, 100)) %>%
  mutate(age = na_if(age, 1000))

clean_2017 <- clean_2017 %>% 
  rename_with(.cols = starts_with("q6_"), .fn = ~str_replace(.x, "q6_", ""))


clean_2017 <- clean_2017 %>%
  mutate(country = str_replace(country, "[u][sS][aA]", "USA")) %>%
  mutate(country = str_replace(country, "[uU][s]", "USA")) %>%
  mutate(country = str_replace(country, "^US$", "USA")) %>%
  mutate(country = str_replace(country, "^Usa$", "USA")) %>%
  mutate(country = str_replace(country, "^USA!", "USA")) %>%
  mutate(country = str_replace(country, "^USA USA USA$", "USA")) %>%
  mutate(country = str_replace(country, "[U][s][a]", "USA")) %>%
  mutate(country = str_replace(country, "^Usa!$", "USA")) %>%
  mutate(country = str_replace(country, "[U][.][S][.][A][.]", "USA")) %>%
  mutate(country = str_replace(country, "^United States of America$", "USA")) %>%
  mutate(country = str_replace(country, "[uU][n][i][t][e][d][ ][Ss][t][a][t][e][s]", "USA")) %>%
  mutate(country = str_replace(country, "^Murica$", "USA")) %>%
  mutate(country = str_replace(country, "^U.S.$", "USA")) %>%
  mutate(country = str_replace(country, "^USA USA! USA!", "USA"))

```

```{r}
# Looking at the differences between the frames - first step to joining

#NOTE TO SELF - stick with 2015 naming



setdiff(names(clean_2016), names(clean_2015))
#whats in x that's NOT in y

# [1] "bonkers_the_candy"                                                                   
#  [2] "bonkers_the_board_game"                                                              
#  [4] "chardonnay"                                                                          
#  [5] "coffee_crisp"                                                                        
#  [6] "dove_bars"                                                                           
#  [7] "hersheys_dark_chocolate"                                                             
#  [8] "hersheys_kisses"                                                                     
#  [9] "licorice_yes_black"                                                                  
# [10] "mike_and_ike"                                                                        
# [11] "blue_m_ms"                                                                           
# [12] "red_m_ms"                                                                            
# [13] "third_party_m_ms"                                                                    
# [14] "mr_goodbar"                                                                          
# [15] "peeps"                                                                               
# [16] "person_of_interest_season_3_dvd_box_set_not_including_disc_4_with_hilarious_outtakes"
# [17] "reeses_pieces"                                                                       
# [18] "sourpatch_kids_i_e_abominations_of_nature"                                           
# [19] "sweet_tarts"                                                                         
# [20] "sweetums_a_friend_to_diabetes"                                                       
# [21] "tic_tacs"                                                                            
# [22] "whatchamacallit_bars"                                                                

2015 = 2016

clean_2016 <- clean_2016 %>%
  rename(box_o_raisins = boxo_raisins,
         = ,
         = ,
         = ,
         = ,
         
         )


names(clean_2015)
names(clean_2016)

         
         
         
         
setdiff(names(clean_2016), names(clean_2017))

```


What is the total number of candy ratings given across the three years.
(Number of candy ratings, not the number of raters. Don’t count missing values)
```{r}
group_by
summarise(across(count))
```

What was the average age of people who are going out trick or treating?
```{r}
filter(going_out = yes)
group_by(age)
summarise(mean(age))
```

What was the average age of people who are not going trick or treating?
```{r}
filter(going_out = no)
group_by(age)
summarise(mean(age))
```


For each of joy, despair and meh, which candy bar received the most of these ratings?
```{r}

```

How many people rated Starburst as despair?
```{r}

```

For the next three questions, count despair as -1, joy as +1, and meh as 0.
What was the most popular candy bar by this rating system for each gender in
the dataset ?
```{r}
filter(f)
group_by(across(all(joy)))
summarise(sum(n))

```

What was the most popular candy bar in each year?
```{r}

```

What was the most popular candy bar by this rating for people in US, Canada,
UK, and all other countries?
```{r}

```

Any other interesting analyses or conclusions you come across.
```{r}
# Not my analysis, but if I have time, I would like to replicate it:
# ://boingboing.net/2015/10/31/the-candy-hierarchy-2015-your.html
# Table 1.B

# EXTENSION
# Step 7. For the "please leave"/"please List" columns, create a coding matrix,
# code the data.
# Step 8. Mints - change all non-numeric data to numeric.
# Step 9. Betty/Ver - Change all ?? to NA.
# Step 10. "Check all that apply" - split columns.
# Step 11. Add NA's to all the "random" columns in the blanks.
```
