---
title: "Dirty Data - Halloween Candy"
output: html_notebook
---
### Louise Shambrook
### 26/11/2021

### Brief Introduction to the dataset
This dataset is based on data from David Ng and Ben Cohen. They have previously ranked candy based on their location in geological strata, for trick or treating purposes. As of 2019, this has become a way of measuring "net feelies" when trick or treating, for a wide range of candies, which critically includes items such as hugs, glow sticks and bread. Source: https://boingboing.net/author/davidng2

### Brief introductions to assumptions
- I intially assumed the dataset was complete, i.e. that the columns were correct (should be there).
- I later assummed some columns could/should be dropped, and then attempted to delete too many.
- I assumed that the columns should remain intact with their data, across the 3 years.
- I assumed that respondents will generally only be from the US and Canada.
- I assumed that age will only be given in whole numbers.
- I assumed that the joined table did not / could not be pivoted, due to the large amount of data collected.

Note a key assumption:
A key focus of the cleaning process has been to retain as much data as possible, with the assumption that in the analysis it will then be possible to filter irrelvant factors (e.g. year, when) this is not pertinent to the question at hand). Therefore, for all questions/answers, it should be assumed that no data has been removed, and where some has been removed, it is judged that this should not have an impact on the final outcome.

### Steps to clean the data
- Using janitor to clean the column names.
- Renaming select variables to ensure that their data could be identified
- Relocating columns
- Changing the timestamp to the year.
- Changing inaccurate age responses to either the given answer (e.g. "40, deal" to 40, or dropping).
- Transforming the age column to numeric.
- Adding missing columns, e.g. gender, or missing candy columns
- Dropping columns, e.g. the columns which surveyed character, as that would not be examined in this analysis
- Renaming columns to align the names across the years
- Setting the order to align the order across the years
- Joining the 3 years together by using bind_rows
- Saving to csv.
- For some of the analysis questions, the dataframe has been manipulated to change JOY, DESPAIR, and MEH to +1, -1 and 0 respectively.

```{r}
# reading in cleaned data and calling required libraries

candy_data_clean_joined <- read_csv(
  here::here("~/GitHub/dirty_data/task_4/dirty_data_codeclan_project_louise/clean_data/joined_candy"))

library(readr)
library(readxl)
library(dplyr)
library(here)
library(janitor)
library(stringr)
library(tidyverse)
library(assertr)
```

### Analysis and answers to questions


### What is the total number of candy ratings given across the three years?
```{r}
total_rating <- function(cheese, banana, cake) {
  rowSums(cheese) + rowSums(banana) + rowSums(cake)
}

total_rating(joy_rating, meh_rating, despair_rating)

```

### What was the average age of people who are going out trick or treating?
```{r}
candy_data_clean_joined %>%
  select(age, going_out) %>%
  filter(going_out == "Yes", (!is.na(age))) %>%
  summarise(mean_age = mean(age))
```

### What was the average age of people who are not going trick or treating?
```{r}
candy_data_clean_joined %>%
  select(age, going_out) %>%
  filter(going_out == "No", (!is.na(age))) %>%
  summarise(mean_age = mean(age))
```

### For each of joy, despair and meh, which candy bar received the most of these ratings?


### joy
```{r}
joy_rating <- candy_data_clean_joined %>%
  select(-year, -going_out, -state, -country, -age, -gender) %>%
  summarise(across(c(hundred_grand_bar,
                  anonymous_brown_globs_that_come_in_black_and_orange_wrappers_a_k_a_mary_janes,
                  any_full_sized_candy_bar,black_jacks,bonkers_the_candy,
                  bonkers_the_board_game, bottle_caps, boxo_raisins, broken_glow_stick,
                  butterfinger, cadbury_creme_eggs, candy_corn, 
                  candy_that_is_clearly_just_the_stuff_given_out_for_free_at_restaurants, 
                  caramellos, cash_or_other_forms_of_legal_tender, chardonnay,
                  chick_o_sticks_we_don_t_know_what_that_is,chiclets,
                  coffee_crisp, creepy_religious_comics_chick_tracts,
                  dental_paraphenalia, dots, dove_bars,fuzzy_peaches,
                  generic_brand_acetaminophen, glow_sticks,goo_goo_clusters,
                  good_n_plenty,gum_from_baseball_cards,
                  gummy_bears_straight_up, hard_candy, healthy_fruit, heath_bar,
                  hersheys_dark_chocolate,hershey_s_milk_chocolate,
                  hersheys_kisses,hugs_actual_physical_hugs,
                  jolly_ranchers_good_flavor, jolly_rancher_bad_flavor,
                  joy_joy_mit_iodine,junior_mints,senior_mints,kale_smoothie,
                  kinder_happy_hippo,kit_kat, laffy_taffy,lemon_heads, licorice_not_black,
                  licorice_yes_black, lindt_truffle, lollipops, mars,
                  maynards, mike_and_ike, milk_duds,milky_way,
                  regular_m_ms,peanut_m_m_s, blue_m_ms,red_m_ms,
                  green_party_m_ms, independent_m_ms,abstained_from_m_ming,
                  minibags_of_chips, mint_kisses, mint_juleps, mr_goodbar,
                  necco_wafers, nerds, nown_laters, peeps, pencils,pixy_stix,
                  real_housewives_of_orange_county_season_9_blue_ray, 
                  reese_s_peanut_butter_cups,reeses_pieces,
                  reggie_jackson_bar,rolos,
                  sandwich_sized_bags_filled_with_boo_berry_crunch,skittles,
                  smarties_american,smarties_commonwealth,snickers,
                  sourpatch_kids_i_e_abominations_of_nature,spotted_dick,
                  starburst,sweet_tarts,swedish_fish,
                  sweetums_a_friend_to_diabetes, take_5, tic_tacs,
                  those_odd_marshmallow_circus_peanut_things, three_musketeers,
                  tolberone_something_or_other, trail_mix,
                  vials_of_pure_high_fructose_corn_syrup_for_main_lining_into_your_vein,
                  twix, vicodin, whatchamacallit_bars, white_bread,
                  whole_wheat_anything, york_peppermint_patties,
                  brach_products_not_including_candy_corn, bubble_gum,
                  hersheys_kissables, lapel_pins, runts, mint_leaves,
                  mint_m_ms, ribbon_candy, peanut_butter_bars, peanut_butter_jars,
                  peterson_brand_sidewalk_chalk, mary_janes, third_party_m_ms,
                  person_of_interest_season_3_dvd_box_set_not_including_disc_4_with_hilarious_outtakes,
                  nestle_crunch), ~sum(.x == "JOY", na.rm = TRUE)))
colnames(joy_rating)[max.col(joy_rating,ties.method="first")]

```


### meh
```{r}
meh_rating <- candy_data_clean_joined %>%
  select(-year, -going_out, -state, -country, -age, -gender) %>%
  summarise(across(c(hundred_grand_bar,
                  anonymous_brown_globs_that_come_in_black_and_orange_wrappers_a_k_a_mary_janes,
                  any_full_sized_candy_bar,black_jacks,bonkers_the_candy,
                  bonkers_the_board_game, bottle_caps, boxo_raisins, broken_glow_stick,
                  butterfinger, cadbury_creme_eggs, candy_corn, 
                  candy_that_is_clearly_just_the_stuff_given_out_for_free_at_restaurants, 
                  caramellos, cash_or_other_forms_of_legal_tender, chardonnay,
                  chick_o_sticks_we_don_t_know_what_that_is,chiclets,
                  coffee_crisp, creepy_religious_comics_chick_tracts,
                  dental_paraphenalia, dots, dove_bars,fuzzy_peaches,
                  generic_brand_acetaminophen, glow_sticks,goo_goo_clusters,
                  good_n_plenty,gum_from_baseball_cards,
                  gummy_bears_straight_up, hard_candy, healthy_fruit, heath_bar,
                  hersheys_dark_chocolate,hershey_s_milk_chocolate,
                  hersheys_kisses,hugs_actual_physical_hugs,
                  jolly_ranchers_good_flavor, jolly_rancher_bad_flavor,
                  joy_joy_mit_iodine,junior_mints,senior_mints,kale_smoothie,
                  kinder_happy_hippo,kit_kat, laffy_taffy,lemon_heads, licorice_not_black,
                  licorice_yes_black, lindt_truffle, lollipops, mars,
                  maynards, mike_and_ike, milk_duds,milky_way,
                  regular_m_ms,peanut_m_m_s, blue_m_ms,red_m_ms,
                  green_party_m_ms, independent_m_ms,abstained_from_m_ming,
                  minibags_of_chips, mint_kisses, mint_juleps, mr_goodbar,
                  necco_wafers, nerds, nown_laters, peeps, pencils,pixy_stix,
                  real_housewives_of_orange_county_season_9_blue_ray, 
                  reese_s_peanut_butter_cups,reeses_pieces,
                  reggie_jackson_bar,rolos,
                  sandwich_sized_bags_filled_with_boo_berry_crunch,skittles,
                  smarties_american,smarties_commonwealth,snickers,
                  sourpatch_kids_i_e_abominations_of_nature,spotted_dick,
                  starburst,sweet_tarts,swedish_fish,
                  sweetums_a_friend_to_diabetes, take_5, tic_tacs,
                  those_odd_marshmallow_circus_peanut_things, three_musketeers,
                  tolberone_something_or_other, trail_mix,
                  vials_of_pure_high_fructose_corn_syrup_for_main_lining_into_your_vein,
                  twix, vicodin, whatchamacallit_bars, white_bread,
                  whole_wheat_anything, york_peppermint_patties,
                  brach_products_not_including_candy_corn, bubble_gum,
                  hersheys_kissables, lapel_pins, runts, mint_leaves,
                  mint_m_ms, ribbon_candy, peanut_butter_bars, peanut_butter_jars,
                  peterson_brand_sidewalk_chalk, mary_janes, third_party_m_ms,
                  person_of_interest_season_3_dvd_box_set_not_including_disc_4_with_hilarious_outtakes,
                  nestle_crunch), ~sum(.x == "MEH", na.rm = TRUE)))
colnames(meh_rating)[max.col(meh_rating,ties.method="first")]

```

### despair
```{r}
despair_rating <- candy_data_clean_joined %>%
  select(-year, -going_out, -state, -country, -age, -gender) %>%
  summarise(across(c(hundred_grand_bar,
                  anonymous_brown_globs_that_come_in_black_and_orange_wrappers_a_k_a_mary_janes,
                  any_full_sized_candy_bar,black_jacks,bonkers_the_candy,
                  bonkers_the_board_game, bottle_caps, boxo_raisins, broken_glow_stick,
                  butterfinger, cadbury_creme_eggs, candy_corn, 
                  candy_that_is_clearly_just_the_stuff_given_out_for_free_at_restaurants, 
                  caramellos, cash_or_other_forms_of_legal_tender, chardonnay,
                  chick_o_sticks_we_don_t_know_what_that_is,chiclets,
                  coffee_crisp, creepy_religious_comics_chick_tracts,
                  dental_paraphenalia, dots, dove_bars,fuzzy_peaches,
                  generic_brand_acetaminophen, glow_sticks,goo_goo_clusters,
                  good_n_plenty,gum_from_baseball_cards,
                  gummy_bears_straight_up, hard_candy, healthy_fruit, heath_bar,
                  hersheys_dark_chocolate,hershey_s_milk_chocolate,
                  hersheys_kisses,hugs_actual_physical_hugs,
                  jolly_ranchers_good_flavor, jolly_rancher_bad_flavor,
                  joy_joy_mit_iodine,junior_mints,senior_mints,kale_smoothie,
                  kinder_happy_hippo,kit_kat, laffy_taffy,lemon_heads, licorice_not_black,
                  licorice_yes_black, lindt_truffle, lollipops, mars,
                  maynards, mike_and_ike, milk_duds,milky_way,
                  regular_m_ms,peanut_m_m_s, blue_m_ms,red_m_ms,
                  green_party_m_ms, independent_m_ms,abstained_from_m_ming,
                  minibags_of_chips, mint_kisses, mint_juleps, mr_goodbar,
                  necco_wafers, nerds, nown_laters, peeps, pencils,pixy_stix,
                  real_housewives_of_orange_county_season_9_blue_ray, 
                  reese_s_peanut_butter_cups,reeses_pieces,
                  reggie_jackson_bar,rolos,
                  sandwich_sized_bags_filled_with_boo_berry_crunch,skittles,
                  smarties_american,smarties_commonwealth,snickers,
                  sourpatch_kids_i_e_abominations_of_nature,spotted_dick,
                  starburst,sweet_tarts,swedish_fish,
                  sweetums_a_friend_to_diabetes, take_5, tic_tacs,
                  those_odd_marshmallow_circus_peanut_things, three_musketeers,
                  tolberone_something_or_other, trail_mix,
                  vials_of_pure_high_fructose_corn_syrup_for_main_lining_into_your_vein,
                  twix, vicodin, whatchamacallit_bars, white_bread,
                  whole_wheat_anything, york_peppermint_patties,
                  brach_products_not_including_candy_corn, bubble_gum,
                  hersheys_kissables, lapel_pins, runts, mint_leaves,
                  mint_m_ms, ribbon_candy, peanut_butter_bars, peanut_butter_jars,
                  peterson_brand_sidewalk_chalk, mary_janes, third_party_m_ms,
                  person_of_interest_season_3_dvd_box_set_not_including_disc_4_with_hilarious_outtakes,
                  nestle_crunch), ~sum(.x == "DESPAIR", na.rm = TRUE)))
colnames(despair_rating)[max.col(despair_rating,ties.method="first")]
```


### How many people rated Starburst as despair?
```{r}
candy_data_clean_joined %>%
  select(starburst)%>%
  filter(starburst == "DESPAIR") %>%
  summarise(starburst_sum = sum(n()))

```

For the next three questions, count despair as -1, joy as +1, and meh as 0.
```{r}
#Adding a variable to answer the following questions with numeric values.
candy_big_numbers <- candy_data_clean_joined %>%
  mutate(across(c(hundred_grand_bar,
                  anonymous_brown_globs_that_come_in_black_and_orange_wrappers_a_k_a_mary_janes,
                  any_full_sized_candy_bar,black_jacks,bonkers_the_candy,
                  bonkers_the_board_game, bottle_caps, boxo_raisins, broken_glow_stick,
                  butterfinger, cadbury_creme_eggs, candy_corn, 
                  candy_that_is_clearly_just_the_stuff_given_out_for_free_at_restaurants, 
                  caramellos, cash_or_other_forms_of_legal_tender, chardonnay,
                  chick_o_sticks_we_don_t_know_what_that_is,chiclets,
                  coffee_crisp, creepy_religious_comics_chick_tracts,
                  dental_paraphenalia, dots, dove_bars,fuzzy_peaches,
                  generic_brand_acetaminophen, glow_sticks,goo_goo_clusters,
                  good_n_plenty,gum_from_baseball_cards,
                  gummy_bears_straight_up, hard_candy, healthy_fruit, heath_bar,
                  hersheys_dark_chocolate,hershey_s_milk_chocolate,
                  hersheys_kisses,hugs_actual_physical_hugs,
                  jolly_ranchers_good_flavor, jolly_rancher_bad_flavor,
                  joy_joy_mit_iodine,junior_mints,senior_mints,kale_smoothie,
                  kinder_happy_hippo,kit_kat, laffy_taffy,lemon_heads, licorice_not_black,
                  licorice_yes_black, lindt_truffle, lollipops, mars,
                  maynards, mike_and_ike, milk_duds,milky_way,
                  regular_m_ms,peanut_m_m_s, blue_m_ms,red_m_ms,
                  green_party_m_ms, independent_m_ms,abstained_from_m_ming,
                  minibags_of_chips, mint_kisses, mint_juleps, mr_goodbar,
                  necco_wafers, nerds, nown_laters, peeps, pencils,pixy_stix,
                  real_housewives_of_orange_county_season_9_blue_ray, 
                  reese_s_peanut_butter_cups,reeses_pieces,
                  reggie_jackson_bar,rolos,
                  sandwich_sized_bags_filled_with_boo_berry_crunch,skittles,
                  smarties_american,smarties_commonwealth,snickers,
                  sourpatch_kids_i_e_abominations_of_nature,spotted_dick,
                  starburst,sweet_tarts,swedish_fish,
                  sweetums_a_friend_to_diabetes, take_5, tic_tacs,
                  those_odd_marshmallow_circus_peanut_things, three_musketeers,
                  tolberone_something_or_other, trail_mix,
                  vials_of_pure_high_fructose_corn_syrup_for_main_lining_into_your_vein,
                  twix, vicodin, whatchamacallit_bars, white_bread,
                  whole_wheat_anything, york_peppermint_patties,
                  brach_products_not_including_candy_corn, bubble_gum,
                  hersheys_kissables, lapel_pins, runts, mint_leaves,
                  mint_m_ms, ribbon_candy, peanut_butter_bars, peanut_butter_jars,
                  peterson_brand_sidewalk_chalk, mary_janes, third_party_m_ms,
                  person_of_interest_season_3_dvd_box_set_not_including_disc_4_with_hilarious_outtakes,
                  nestle_crunch),
                ~recode(.x, "JOY" = 1, "MEH" = 0, "DESPAIR" = -1), na.rm = TRUE, as.numeric(.x)))
```

### What was the most popular candy bar by this rating system for each gender in the dataset ?

### female
```{r}
female_candy_rank <- candy_big_numbers %>%
  select(-year, -going_out, -state, -country, -age) %>%
  filter(gender == "Female") %>%
  summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE)))
  colnames(female_candy_rank)[max.col(female_candy_rank,ties.method="first")]

```

### male
```{r}
male_candy_rank <- candy_big_numbers %>%
  select(-year, -going_out, -state, -country, -age) %>%
  filter(gender == "male") %>%
  summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE)))
colnames(male_candy_rank)[max.col(male_candy_rank,ties.method="first")]
```

### What was the most popular candy bar in each year?

### 2015
```{r}
candy_2015_selected <- candy_big_numbers %>%
  filter(year == 2015)

popular_2015 <- candy_2015_selected %>%
  select(-year, -going_out, -state, -country, -age, -gender) %>%
  summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE)))

colnames(popular_2015)[max.col(popular_2015,ties.method="first")]

```

### 2016
```{r}
candy_2016_selected <- candy_big_numbers %>%
  filter(year == 2016)

popular_2016 <- candy_2016_selected %>%
  select(-year, -going_out, -state, -country, -age, -gender) %>%
  summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE)))

colnames(popular_2016)[max.col(popular_2016,ties.method="first")]
```

### 2017
```{r}
candy_2017_selected <- candy_big_numbers %>%
  filter(year == 2017)

popular_2017 <- candy_2017_selected %>%
  select(-year, -going_out, -state, -country, -age, -gender) %>%
  summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE)))

colnames(popular_2017)[max.col(popular_2017,ties.method="first")]
```


### What was the most popular candy bar by this rating for people in US, Canada, UK, and all other countries?

Note - during the data cleaning process, it was not possible to correct every 
answer for the US, UK and Canada, respectively. There were about 10-15 responses
which remained dirty, and this could therefore skew the answers.
There were also some countries under "other" which were not cleaned; the dirty
quantity is also around 10-15 which could also impact the results.

### US
```{r}
# for the USA
popular_USA <- candy_big_numbers %>%
  select(-gender, -going_out, -state, -year, -age) %>%
  filter(country == "USA") %>%
  summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE)))
colnames(popular_USA)[max.col(popular_USA,ties.method="first")]
```

### Canada
```{r}
popular_canada <- candy_big_numbers %>%
  select(-gender, -going_out, -state, -year, -age) %>%
  filter(country == "Canada") %>%
  summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE)))
colnames(popular_canada)[max.col(popular_canada,ties.method="first")]
```

### UK
```{r}
popular_UK <- candy_big_numbers %>%
  select(-gender, -going_out, -state, -year, -age) %>%
  filter(country == "UK") %>%
  summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE)))
colnames(popular_UK)[max.col(popular_UK,ties.method="first")]
```

### other countries
```{r}
popular_other_countries <- candy_big_numbers %>%
  select(-gender, -going_out, -state, -year, -age) %>%
  filter(country != "Canada", country != "UK", country != "USA") %>%
  summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE)))
colnames(popular_other_countries)[max.col(popular_other_countries,ties.method="first")]
```

### Any other interesting analyses or conclusions you come across.
The research that the original researchers have done on whether a measure of character has an impact on their candy rating is interesting.
I find it curious (concering?) that the same result comes out nearly always on top, i.e. "any full sized any candy", however, given the measure of how I assume this data has been captured, people could be ticking this option, whilst also specifying their chosen candy bar, or not.

Side-note; I was concerned whether my analysis was correct. Therefore I checked the source material. Indeed, any full-sized candy bar ranks on top as of 2019 which aligns with my results.

